openarchaeoCollaboration

### 2021-06-16 analysis/paper.Rmd
Revise contrib distribution figure

```{r plot-contrib-dist}
oarch %>% 
  unnest(gh_contribs) %>% 
  drop_na(contributor) %>% 
  group_by(item_name) %>% 
  mutate(n_contributors = n()) %>% 
  filter(n_contributors > 1) %>% 
  mutate(big_boy = ifelse(contributions == max(contributions), 
                          "Main contributor", "Other contributors")) %>% 
  ggplot(aes(x = item_name, y = contributions, 
             group = contributor,
             fill = big_boy)) +
  geom_col(position = "fill", colour = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Repository", y = "Contributions",
       fill = NULL) +
  coord_flip() +
  theme_oarch() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

>>>>

```{r plot-contrib-dist}
oarch %>% 
  unnest(gh_contribs) %>% 
  drop_na(contributor) %>% 
  group_by(item_name) %>% 
  mutate(n_contributors = n()) %>% 
  filter(n_contributors > 1) %>% 
  mutate(big_boy = ifelse(contributions == max(contributions), 
                          "Main contributor", "Other contributors"),
         big_boy_pct = max(contributions) / sum(contributions)) ->x %>% 
  ggplot(aes(x = fct_reorder(item_name, big_boy_pct, .desc = FALSE),
             y = contributions, 
             # group = contributor,
             fill = fct_relevel(big_boy, c("Other contributors",
                                           "Main contributor")))) +
  geom_col(position = "fill", colour = "white", size = 0.1) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_contrast(guide = guide_legend(reverse = TRUE)) +
  labs(title = "Repository contributors by proportion of contributions",
       x = NULL, y = "Contributions",
       fill = NULL,
       caption = "Data: open-archaeo.info and GitHub API") +
  coord_flip() +
  theme_oarch() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )
